\documentclass[11pt,a4paper,numbers=enddot]{scrartcl}
\usepackage{rawfonts}
\usepackage{amssymb}
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,267mm},
 left=25mm,
 top=20mm,
 bottom=20mm,
 right=25mm
  }

\usepackage{color}
\definecolor{astral}{RGB}{46,116,181}
\definecolor{myblue}{rgb}{0.25,0.25,0.5}

\usepackage{sectsty}
\sectionfont{\color{astral}}

\usepackage[colorlinks=true, urlcolor=blue, linkcolor=blue]{hyperref}

\setlength{\parskip}{1.5ex plus 0.5ex minus 0.5ex}
\usepackage{indentfirst}

\begin{document}

\title{\color{myblue}{LookingFor 2.0}}
\subtitle{\color{myblue}{A Masm64 tool to find strings in files}}

\author{Héctor S. Enrique}
\date{ nov 10, 2024}
\maketitle

\section{Running the Program: }

    \begin{itemize}
        \item Step 1: Enter target, that is a path and some file mask, for example:
         
        \verb$              $ Target: \verb$\Masm64\*.as?|*.inc$. 
        
	\hspace{1cm} where:\\
        \verb$              $ Target Path: \verb$\Masm64\     $  (end with backslash character ``\verb$\$'') \\
        \verb$              $ Target Mask: \verb$*.as?|*.inc  $  (can't be empty, at least a wildcard ``\verb$*$'') 
        
        \item Step 2: Enter strings to search. If no string is entered then all files that fit the mask are listed. If there are two strings, files listed match both.
        \item Step 3: For each string set modes to search:
        
    \begin{itemize}
	 \item case: sensitive, insensitive or ignore first char.
	 \item word: partial word, full word, or full with underscore (usually a compose word). An experimental options is full with points (because ML64 accept the point at name beginning).
     \end{itemize}
        \item Step 4:  If You want to exclude files fitting some mask, write that in ``excluded'' cell (for example \verb$*.exe|*.lib|*.dll|*.obj$)
        \item Step 5 : When entered two strings, is possible to restrict the search to some distance between them. Enter in cell ``maxDist'' the number of bytes.
        \item Step 6 : Adittionally, files to search can be limited by size writing megabyte size in cell ``maxMb''.
        \item Step 7 : Click ``Find'' button (or Return key in any edition cell).
        \item Step 8 : a running search can be stopped any moment clicking same button, wich now show ``Cancel'' text.
     \end{itemize}


\section{Values storage: }

	After first running the program will create an .ini file containing:
	
    \begin{itemize}
	\item Key 1: interface size and position    	
	\item Key 2: to store current target and search parameters.
	\item Key 3: prefered list of targets (see \hyperlink{targets}{Targets List}).
	\item Key 4: default editors for \verb$*.bat$, \verb$*.cmd$ and \verb$*.js$ files (if not present \verb$\masm64\qeditor$).
	\item Key 5: last sorting order.
    \end{itemize}

\section {More about file mask}

	Some general file masks can be used to search:
	
	\hspace{2cm}``*``  in all files, except ``.`` and ``..``
	
	\hspace{2cm}``*.`` in files without extension

	\hspace{2cm}``.*`` in only extension files 

	\hspace{2cm}``*.*`` in all files with name and extension
	
\section {Files matching definitions}
	
	Clicking with mouse or pressing Enter key will open selected file in result list. Because is a tool for programming, is expected that extensions of interest have associated an editor.
	
	Executable files will not open to prevent unwanted runnings. 
	
	In similar way \verb$*.bat$, \verb$*.cmd$ and \verb$*.js$ files will not run. But in this cases they will open in an editor. By default \verb$\masm64\qeditor$ is that editor. But is possible to select a new path or editor. If default or stored editor fail, a dialog will ask a new path or editor. Later, editor could be changed in LookingFor.ini file.

\hypertarget{targets}{}\section {Targets List} 
	
	Buttons ``+'' and ``--'' allow to store or remove current target from an specific list stored in LookingFor.ini file. 
	
	Button ``...'' open a dialog with options to sort the targets by storage sequence, characters in target and use frequency, in ascendent or descent order. The ASCII characters are ordered as following: symbols (first half), numbers, letters (case insensible), second half characters (above 127). 
	
	
\section{Knowledgements}

	To Masm32 forum members that help in testing this application, specially to greenozon for detailed reports.

\section{Additional Information}

	The program was builded with \verb$Masm64 SDK$.

	Source code and discussion is is available at:
    \begin{itemize}
	
	\item \href{https://masm32.com/board/index.php?topic=11888.0}{LookingFor: a Masm64 tool to find strings in files} (in Masm32 Forum) 
	\item \href{https://github.com/ASMHSE/LookingFor-in-Assembly}{LookingFor\_in\_Assembly} (in GitHub) 
     \end{itemize}
	


\end{document}